---
title: "intermediate investigation on parchment data"
output:
  pdf_document: default
  html_document:
    df_print: paged
date: "2022-10-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
rm(list = ls())
source('./Functions.R')
#load('../Rdata/blast_result_withY.Rdata')
library(scater) # from bioconductor
library(patchwork)
set.seed(256)
```

# Reference file name

**Genome assembly ARS-LIC_NZ_Holstein-Friesian_1**

```{r, include=FALSE}
# read data
results_ref1 = read.blast('../ref_withY')
results = read.blast('../ref_withY2') 

#save.image(file = '../Rdata/blast_result_withY.Rdata')
```

# percentage of identity V.S. coverage among 22 samples.

**sample SG-LibNeg_S10_L001_R1_001 and SG-LibNeg_S10_L001_R2_001 have few hits that are not informative. Therefore, they are removed**

```{r, echo=FALSE}
results = results %>% group_by(sample_name) %>% filter(n()>100)
results = results %>% filter(pident>96, length>110, evalue < 1e-10)
ggplot(data = results, aes(x=pident, y=length)) +
  geom_hex(bins = 40) +
  scale_fill_continuous(type = "viridis") +
  theme_bw() +
  facet_wrap(~sample_name) +
  labs(title = 'percentage of identity v.s. coverage',
       subtitle = 'pident>96, length>110, evalue < 1e-10')

```

# Number of autosomal chromosome hits V.S. number of Y chromosome hits

```{r, echo=FALSE}
# # ref1
# X = 'NC_007331.5'
# Y ='NC_016145.1'
# ref2
X = 'CM038108.1'
Y = 'CM038109.1'
n_autosomal_chromosome = results %>% filter(sseqid != X & sseqid != Y) %>% dplyr::count(sample_name)
n_Y_chromosome = results %>% filter(sseqid == Y) %>% dplyr::count(sample_name)
autoVSy = merge(n_autosomal_chromosome, n_Y_chromosome, by = "sample_name")
colnames(autoVSy) = c('sample','autosomal','Y')

p1 = ggplot(data = autoVSy, aes(x = autosomal, y=Y)) +
  geom_point()+
  labs(title = 'number of hits in Y chromosome v.s. number of hits in autosomal chromosome')
p2 = ggplot(data = autoVSy, aes(x = autosomal, y=Y, label = sample)) +
  geom_label()
p1/p2 

```

# map of hits in Y chromosome reference sequence

x dots are projections of the curve on x axis

```{r, echo=FALSE}
Y_chromosome = results %>% filter(sseqid == Y)
df = Y_chromosome[order(Y_chromosome$sstart),]
ggplot(data = df) + 
  geom_point(aes(x=sstart, y=1:dim(df)[1], colour = 'start'), size = 2) +
  geom_point(aes(x=send, y=1:dim(df)[1], colour = 'end'), size = 0.5) +
  geom_point(aes(x = sstart, y = 0)) +
  geom_point(aes(x = send, y = 0)) +
  xlab('position in reference sequence') +
  ylab('sorted hit number by sstart') +
  facet_wrap(~sample_name) +
  ggplot(data = df) + 
  geom_point(aes(x=sstart, y=1:dim(df)[1], colour = 'start'), size = 2) +
  geom_point(aes(x=send, y=1:dim(df)[1], colour = 'end'), size = 0.5) +
  geom_point(aes(x = sstart, y = 0)) +
  geom_point(aes(x = send, y = 0)) +
  xlab('position in reference sequence') +
  ylab('sorted hit number by sstart') 
```

```{r, include=FALSE}
# x = Y_chromosome[order(Y_chromosome$length, decreasing = F),]
# x=x %>% filter(sample_name == 'SG-047_S3_L001_R1_001')
# levels(factor(results$sample_name))
results_ref1 = read.blast('../ref_withY')
results = read.blast('../ref_withY2') 
# ref1
X = 'NC_007331.5'
Y = 'NC_016145.1'

Y_chromosome = results_ref1 %>% filter(sseqid == Y)
df = Y_chromosome[order(Y_chromosome$sstart),]

p1 = ggplot(data = df) + 
  geom_point(aes(x=sstart, y=1:dim(df)[1], colour = 'start'), size = 2) +
  geom_point(aes(x=send, y=1:dim(df)[1], colour = 'end'), size = 0.5) +
  geom_point(aes(x = sstart, y = 0)) +
  geom_point(aes(x = send, y = 0)) +
  xlab('position in reference sequence') +
  ylab('sorted hit number by sstart') +
  ggtitle('reference genome: Btau_5.0.1')

df = Y_chromosome

p2 = ggplot(data = df) + 
  geom_point(aes(x=sstart, y=1:dim(df)[1], colour = 'start'), size = 2) +
  geom_point(aes(x=send, y=1:dim(df)[1], colour = 'end'), size = 0.5) +
  geom_point(aes(x = sstart, y = 0)) +
  geom_point(aes(x = send, y = 0)) +
  xlab('position in reference sequence') +
  ylab('hit number by sstart') 

p1+p2

# ref2
X = 'CM038108.1'
Y = 'CM038109.1'

Y_chromosome = results %>% filter(sseqid == Y)
df = Y_chromosome[order(Y_chromosome$sstart),]

p3 = ggplot(data = df) + 
  geom_point(aes(x=sstart, y=1:dim(df)[1], colour = 'start'), size = 2) +
  geom_point(aes(x=send, y=1:dim(df)[1], colour = 'end'), size = 0.5) +
  geom_point(aes(x = sstart, y = 0)) +
  geom_point(aes(x = send, y = 0)) +
  xlab('position in reference sequence') +
  ylab('sorted hit number by sstart') +
  ggtitle('ARS-LIC_NZ_Holstein-Friesian_1')

df = Y_chromosome

p4 = ggplot(data = df) + 
  geom_point(aes(x=sstart, y=1:dim(df)[1], colour = 'start'), size = 2) +
  geom_point(aes(x=send, y=1:dim(df)[1], colour = 'end'), size = 0.5) +
  geom_point(aes(x = sstart, y = 0)) +
  geom_point(aes(x = send, y = 0)) +
  xlab('position in reference sequence') +
  ylab('hit number by sstart') 


p3+p4
```
